Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2020-07-26 inst/manuscript/analyses-mapreference-sample.Rmd
Update through analysis and reshaping of iteration_metrics

# sample size function
ref_sample_size <- function(p, z, d) {
  n <- (z^2 * p * (1 - p)) / d^2
  data.frame(p = p, n = n)
}

@@

Remove all points that were used for training, training referenec, or  validation. Contained in CSV of sites prepared in `data_prep.R`
```{r, eval = FALSE}
train_val <- readr::read_csv(here("external/data/train_val_sites.csv"))
fpointsr <- fpoints %>% filter(!id %in% unique(train_val$id))
```

>>>>

###! Move this to SI
# sample size function
ref_sample_size <- function(p, z, d) {
  n <- (z^2 * p * (1 - p)) / d^2
  data.frame(p = p, n = n)
}

@@

Remove all points that were used for training, training reference, or  validation. Contained in CSV of sites prepared in `data_prep.R`
```{r, eval = FALSE}
train_val <- readr::read_csv(here("external/data/train_val_sites.csv"))
fpointsr <- fpoints %>% filter(!id %in% unique(train_val$id))
```

### 2020-07-26 inst/manuscript/analyses.Rmd
Update through analysis and reshaping of iteration_metrics

# Rename one of two AOI3 results, and then bind
fpoints[[3]] <- fpoints[[3]] %>% mutate(aoi = "3N")
fpoints <- do.call(rbind, fpoints)
xy <- fpoints %>% st_coordinates() %>% as_tibble() %>% rename(x = X, y = Y)
fpoints_tb <- bind_cols(fpoints %>% as_tibble() %>% select(-geometry), xy)
# data.table::fwrite(
#   fpoints_tb, file = here("external/data/field_points005.csv")
# )

>>>>

# Rename one of two AOI3 results, and then bind
fpoints[[3]] <- fpoints[[3]] %>% mutate(aoi = "3N")
fpoints <- do.call(rbind, fpoints)
xy <- fpoints %>% st_coordinates() %>% as_tibble() %>% rename(x = X, y = Y)
fpoints_tb <- bind_cols(fpoints %>% as_tibble() %>% select(-geometry), xy)

# data.table::fwrite(
#   fpoints_tb, file = here("external/data/field_points005.csv")
# )

### 2020-07-26 inst/manuscript/manuscript.Rmd
Update through analysis and reshaping of iteration_metrics

Where $\theta$ represents the true cover type of a pixel (field or not field), *D* is the worker's label of that field, and $W_i$ is an individual worker.  P($\theta$|D) is therefore the probability that the actual cover type is what the workers who labelled it says it is, while P(W$_i$|D) is the worker's average score over the accuracy assessment assignments they have mapped to date, and P(W$\theta$|D, *W$_i$*) is the worker's label for that pixel. This approach therefore uses the overall accuracy of each worker to weight their labels as they are combined with other workers' labels for a given pixel (see SI for further details). The Bayesian risk of the completed final is then assessed, which measures the average level of consensus for the label assigned to each pixel in a given site, with values closer to 0 indicating complete consensus, and thus the highest confidence, while values approaching 1 reveal progressively increasing disagreement (see SI).

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data("label_summary")  
tsites <- label_summary$nlabels %>% group_by(kml_type) %>% 
  summarize(tot = sum(n), mu = round(mean(n)), med = round(median(n)), 
            stdev = round(sd(n)), lower = min(n), upper = max(n))

# training rate
train_rate <- label_summary$nlabels %>% 
  tidyr::pivot_wider(names_from = kml_type, values_from = n) %>% 
  rename_all(funs(c("ID", "tr", "tref"))) %>% 
  mutate(trate = tref / tr)
```

@@

After each site was mapped by four labellers, consensus labels were generated.

### Model performance

>>>>

Where $\theta$ represents the true cover type of a pixel (field or not field), *D* is the worker's label of that field, and $W_i$ is an individual worker.  P($\theta$|D) is therefore the probability that the actual cover type is what the workers who labelled it says it is, while P(W$_i$|D) is the worker's average score over the accuracy assessment assignments they have mapped to date, and P(W$\theta$|D, *W$_i$*) is the worker's label for that pixel. This approach therefore uses the overall accuracy of each worker to weight their labels as they are combined with other workers' labels for a given pixel (see SI for further details). **The "risk" of the final consensus label is then assessed, which measures the proportion of pixels in the label exceeding a Bayesian risk threshold (see SI), and thus provides an additional measure of label quality.**

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data("label_summary")  
toofew <- label_summary$nlabels %>% filter(n < 10) %>% pull(ID)
tsites <- label_summary$nlabels %>% filter(!ID %in% toofew) %>% 
  group_by(kml_type) %>% 
  summarize(tot = sum(n), mu = round(mean(n)), med = round(median(n)), 
            stdev = round(sd(n)), lower = min(n), upper = max(n))

# training rate
train_rate <- label_summary$nlabels %>% 
  tidyr::pivot_wider(names_from = kml_type, values_from = n) %>% 
  rename_all(funs(c("ID", "tr", "tref"))) %>% 
  mutate(trate = tref / tr) %>% filter(tr > 10)
```

@@

After each site was mapped by four labellers, consensus labels were generated. **The average risk for each consensus label was *X* (see SI)**.

### Model performance
The average performance associated

### 2020-07-26 inst/manuscript/si.Rmd
Update through analysis and reshaping of iteration_metrics

After creating the consensus label, the degree of confidence in the resulting label value can be expressed in terms of Bayesian risk. Risk for a given training sample site *i* is calculated as:

\begin{equation}
\mathrm{R_i=\frac{1}{n}\sum_{j=1}^{n} C_j(1 - L_j) + (1 - C_j)L_j}
\end{equation}

@@

$$
Weight_A = score_A * PA_A(field) = P(W_A)P(D=field|W_A) = `r sc[1, 2]` * `r sc[1, 4]` = `r wtA`
$$

@@

Using the relevant part of equation 15, T=the corresponding risk associated with this particular pixel's label $\mathrm{R_j}$ is thus `r rj * (1 - 1) + (1 - rj) * 1`.

@@

The distribution of data collection effort and scores received at training reference sites by labelling team (Figure \ref{fig:trainqual}).

```{r trainqual, echo = FALSE, out.width="60%", fig.cap="The A) distributions of scores at training reference sites for each labeller (means indicated by X in boxplots), and B) the number of training and training reference sites completed by each labeller. Labellers' identities are anonymized.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_training_quality_n.png')
```

>>>>

After creating the consensus label, the degree of confidence in the resulting label value can be expressed in terms of Bayesian risk. Risk is calculated as:

\begin{equation} \label{eq:pixelrisk}
\mathrm{r=C(1 - L) + (1 - C)L}
\end{equation}

Where *C* is the consensus probability that a given pixel is a field ($\mathrm{P(\theta = field|D)}$), and *L* is the consensus label (i.e. non-field if *C* < 0.5, field if *C* > 0.5) for that pixel. The risk values across the entire sample site can be processed in two ways to provide useful information about the confidence in the consensus label for that site. The first is a simple average of all risk values in the site, where the slope of the risk varies depending on whether *L* is a field or not a field (Figure \ref{fig:riskcurve}). The closer to 0 the lower the risk that the *L* is mislabelled, while values approaching 1 indicate increasing risk of mislabelling. A second approach is to calculate the proportion of pixels having risk values that exceed a certain threshold. This second approach is currently implemented in our system, using a threshold value of 0.4.

@@

\clearpage
$$
Weight_A = score_A * PA_A(field) = P(W_A)P(D=field|W_A) = `r sc[1, 2]` * `r sc[1, 4]` = `r wtA`
$$

@@

Using equation \ref{eq:pixelrisk}, the corresponding risk associated with this particular pixel's label is thus `r rj * (1 - 1) + (1 - rj) * 1`.

@@

The distribution of data collection effort and scores received at training reference sites by labelling team (Figure \ref{fig:trainqual}). These results include those from a repeated labelling of the initial training in Cluster 2.  This was done because we discovered a small spatial offset in the original image composites, which we corrected by reprocessing the images. We replaced the image overlays in the instance for Cluster 2 \ref{fig:trainval}A), and the labelling team mapped these sites a second time during the production run in late 2019. The reprocessed labels were used to initially train the model for AOIs 9, 12, and 15.

```{r trainqual, echo = FALSE, out.width="60%", fig.cap="The A) distributions of scores at training reference sites for each labeller (means indicated by X in boxplots), and B) the number of training and training reference sites completed by each labeller. Labellers' identities are anonymized.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_training_qual_n.png')
```
